---
title: "Food Oral Immunotherapy (OTI)"
output: 
  pdf_document:
     toc: true
     number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Trial Design

We will assess a binary outcome with an oral food challenge at 18 months by looking at non-inferiority of low and very low dose Oral Immunotherapy (OIT) vs standard dose with (i) 3 arms and (ii) 2 arms if we cut out the very low dose arm. We expected 75% ‘pass’ the challenge at 18-month and define non-inferiority as an absolute difference of 15% between low dose/and very low dose OIT vs standard dose. 


## Randomisation and Sample Size

Assignment is 1:1:1 across the 3 arms. Use a single look at the data after 90 (or 120) kids have reached their 18 month of follow-up.


# Model

Let $Y_{i}$ be the binary outcome of the $i$th participant that represents the desensitisation with an oral food challenge at 18 months and let $\theta$ be the corresponsing success rate. Thus we write the binomial model: 
\begin{eqnarray}
\mathbf{Y}|\theta &\sim& Bino(n,\theta) \\
\theta &\sim& Beta(a,b)\\
\theta|\mathbf{Y} &\sim& Beta(a+y,b+n-y)
\end{eqnarray}

## Bayesian Decision Rule

The parameter of interest is $\theta$ and we define the decision criterion using posterior probability of non-inferiority, 
\begin{eqnarray}
P=Pr(\theta > \theta_s - \delta |\mathbf{Y})
\end{eqnarray}
where, $\theta_s$ is the success rate for standard dose and $\delta$ is the threshold margin. 
Based in the decision criterion, we define the decision rule that $\theta$ is non-inferior if $P > \epsilon_1$ and inferior if $P < \epsilon_0$.


## Trial Simulation Parameters (Operating Characteristics)

Values for $\theta$ is considered from 0.6 to 0.9 with an increment of 0.05.

```{r, echo=FALSE}
n_theta <- cbind(seq(0.60,0.90,by=0.05), seq(0.60,0.90,by=0.05), seq(0.60,0.90,by=0.05))
n_theta
```
The threshold non-inferiority margin is considered as: $\delta = 0.10, 0.15, 0.20$; and the parameters for the decision rule is considered as: $\epsilon_0 = 0.025, 0.050, 0.100$; $\epsilon_1 = 0.975, 0.950, 0.900$.

We use a non-informative prior distribution for $\theta$ by considering the hyper-parameters $a=b=1$. 
```{r priorplot, echo=FALSE}
set.seed(12)
plot(density(rbeta(10000,1,1)),main="Beta(1,1) prior",xlab="")
```

## Sample size 90

(i) 30 participants in each arm for a 3-arm trial and (ii) 45 participants per arm for a 2-arm trial, if we cut out the very low dose arm. 

## Sample size 120

(i) 40 participants in each arm for a 3-arm trial and (ii) 60 participants per arm for a 2-arm trial, if we cut out the very low dose arm. 

